\section{Onset Detection}
This chapter  will cover the anatomy of a segmentation.
In short an onset is the start of a sound event \citep{ACA}. 
A important thing to know about this segmentation is the difference between: transients onset and attack. 
Attack: attack of a note is the time during amplitude changes, from the beginning to the maximum amplitude is reached \citep{ACA}.
Transient: Transient also starts when the attack starts, at the beginning of of a sound. it ends when the note reaches its quasi-periodic state \citep{ACA}.
Onset: Onset is a chosen instant which marks the temporally extended transient \citep{Bello2005}. Mostly that interval is as mentioned earlier, the beginning of a sound. 
\\
There are at lot of different ways of finding onset detection for a audio signals, it depends on which kind of audio signal you have.
In: An Introduction to Audio Content Analysis, \citep{ACA} Lerch refers to three different onset times namely: Note Onset Time (NOT), Acoustic Onset Time (AOT) and Perceptual Onset Time (POT).
\\
NOT: "the time when the instrument is triggered to make a sound.(...) this is not necessarily the time when the signal becomes detectable or audible" \citep{ACA}.
\\
AOT: "the first time when a signal or an acoustic event is theoretically measurable. Sometimes the AOT is called physical onset time" \citep{ACA}.
\\
POT: "the first time when the event can be perceived by the
listener" \citep{ACA}.
\\
So which of these three would be detectable in the signal and be best for automatic onset detection. Since NOT has a symbolic nature, it is cannot be detected by the audio signal. By assuming that the timing to the sound perception is adapted and the audio content analysis (ACA) system used analyses the perceptible audio content, then POT would fit the requirements best\cite{ACA}.

In our project we can use this segmentation to see which part of the audio file have sound, and where there is no sound. 
